\textcolor[rgb]{0,0,1}{Data-Driven Model Predictive Control using Random Forests for Building Energy Optimization and Climate Control}

### 2018-01-22 paper/final/main.tex
reviewed Intro, Sec 2,3,4,5, conclusion and appendix
small changes

\author[FSaddress,EC]{Francesco Smarra\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{francesco.smarra@univaq.it}

@@

\begin{keyword}
Demand response, energy efficiency, predictive control, machine learning, EnergyPlus modeling, real application
\end{keyword}

@@

@@

\appendix
\input{appendixRegTrees.tex}
\end{document}

>>>>

\author[FSaddress,AJaddress,EC]{Francesco Smarra\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{francesco.smarra@univaq.it}
\ead{fsmarra@seas.upenn.edu}

@@

\begin{keyword}
Energy efficiency, energy saving, energy system analysis, energy system simulation, energy system modeling, energy system and automation, sustainable buildings.
\end{keyword}

@@

\appendix
\input{appendixRegTrees.tex}

@@

\end{document}
